### 2019-09-04 manuscript/manuscript.tex
G's changes

\begin{center}
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 10 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
\end{tabular}
\end{center}

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated a bias-corrected
genome-wide $6 \times 6$ temporal covariance matrix $\mathbf{Q}$ for each of
the ten replicates (see Supplementary Material Sections
\ref{supp:ind-depth-var-corr} and \ref{supp:matrix-correction} for details on
the bias correction). Since the \textcite{Barghi2019-qy} study sequenced each
replicate population every ten generations, we calculate the temporal
covariance matrix over ten-generation allele frequency changes, which we write
as $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$. The diagonal elements of
this temporal covariance matrix are the sum of all variances in allele
frequency changes and pairwise covariances, e.g. element $\mathbf{Q}_{t,t} =
\sum_{i=t}^{9} \var(\Delta p_i) + 2\sum_{i \ne j} \cov(\Delta p_i, \Delta
p_j)$. Each off-diagonal element $\mathbf{Q}_{t,s}, \; t \ne s$ contains the
sum of pairwise covariances, $\mathbf{Q}_{t,s} = \sum_{i=t}^{t+9}
\sum_{j=s}^{s+9} \cov(\Delta p_i, \Delta p_j)$ (see Supplementary Material
Section \ref{supp:barghi-covs} for more details). These off-diagonal
covariances are expected to be zero when only drift is acting in the
population, as only linked selection can create covariance between allele
frequency changes \parencite{Buffalo2019-io}. Furthermore, since we cannot
directly observe the temporal covariances between adjacent timepoints, but only
the sums of temporal covariances, we expect the off-diagonal elements of
$\mathbf{Q}$ to be weak. This is because the magnitude of a temporal covariance
$\cov(\Delta p_i, \Delta p_j)$ is governed by the level of additive genetic
variance and linkage disequilibrium that persists after $|i-j|$ generations of
decay, which in \textcite{Barghi2019-qy}'s study design is on average 10
generations.

@@

Still, averaging across the ten temporal covariances matrices, we find positive
temporal covariances across time that are statistically significant (95\% block
bootstraps for all first off-diagonal elements do not contain zero), consistent
with linked selection perturbing allele frequency changes over very short time
periods. We visualize these covariances in Figure \label{figure-1} (A), which
depicts the temporal covariances through time, for each of the five
off-diagonal rows temporal covariance matrix. Each row represents the temporal
covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between some initial
reference generation $s$ (the row of the matrix), and some later timepoint $t$
(the column of the matrix). For each row, the covariances at first are
positive, and then decay towards zero as expected when directional selection
affects linked variants' frequency trajectories until ultimately linkage
disequilibrium and additive genetic variance for decay
\parencite{Buffalo2019-io}. Note that per replicate, the signal is a bit
noisier; see Supplementary Figures XXX.

@@

The replicate design of \textcite{Barghi2019-qy} also allows us to quantify
another covariance: the covariance in allele frequency change between replicate
populations experiencing convergent selection pressure. These between-replicate
covariances are created in the same way as temporal covariances are: neutral
alleles linked to a particular fitness background experience are expected to
have allele frequency changes in the same direction if the selection pressures
are similar. We measure this through a statistic similar to a correlation,
which we call the convergent correlation; this is the ratio of average
between-replicate covariance across all pairs to the average standard deviation
across all pairs of replicates,

@@

We've calculated the convergent correlation for all rows of the replicate
covariance matrices, which unlike temporal covariance matrices have diagonal
elements that are also covariances (e.g. $\cov(\Delta_{_{10}} p_{t,A},
\Delta_{_{10}} p_{t,B})$). Like temporal covariances, we visualize these
through time (Figure \ref{fig:figure-2} A), with each line representing the
convergent correlation from a particular reference generation $s$ as it varies
with $t$ (shown on the x-axis). In other words, each of the colored lines
corresponds to the like colored row of the convergence correlation matrix
(upper left in Figure \ref{fig:figure-2} A). We find these decay very quickly,
from an initial convergence correlation coefficient of about 0.1 (95\% block
bootstrap confidence intervals $[0.094,  0.11]$), to around 0.01 (95\% CIs
[0.0087, 0.015]) within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate populations of
\emph{Drosophila simulans} for 14 generations in a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$).

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows (mean loci per
window 4,606, median 4,830). While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

\gc{It is unclear how strong the fluctuations would have to be to
  generate a genome-wide average signal of fluctuating selection from
  temporal covariances. For example,there many loci could still show a
  signal of fluctuating selection, but their average signals could be
  overwhelmed by other signals of fluctuating selection. To
  investigate whether there was an genome-wide excess} of loci showing evidence
  of fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \gc{\textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy},\gc{the bionomial null model does not
  include random evolutionary variation in allele frequencies. }
% =======
% We were concerned that this might be due to a flaw in our methods. To address
% this concern, we first ensured that our temporal-covariance matrix bias
% correction was working as expected. We find that it corrects the relationship
% between depth and both variance and covariance (Supplementary Figure
% \ref{suppfig:bergland-correction}) as expected. We then re-analyzed the data of
% \parencite{Bergland2014-ij} using the same seasonal fluctuating model as the
% original paper. This model is a Binomial logit-linked GLM fit per-locus, where
% the Spring/Fall seasons are encoded as a dummy variable, and are regressed on
% the frequency data. We use the same binomial weighting procedure as
% \textcite{Bergland2014-ij}, where the weights are determined by the effective
% number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and
% $d_t$ are the number of diploid individuals and the read depth at timepoint
% $t$, respectively). We fit this model on all loci marked as used in the VCF
% provided with the \textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p).
% Overall, our p-values for the Wald test for each locus closely match those of
% the original paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times
% 10^{-16}$; see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison}
% A), and the histograms of the p-values are nearly identical (Supplementary
% Figure \ref{suppfig:bergland-pvalue-comparison} B). 
% >>>>>>> d95c3549a10dc0037f40a54cb8b41f9d412ed1ed

@@

  \caption{The variance and covariances from the \texticite{Bergland2014-ij}
    study, calculated in 100kb genomic windows plotted against average depth in
    a window before and after bias correction. Each panel has a least-squares
    estimate between the variance and covariance, and the average depth.
    The bias correction procedure is correcting sampling bias in both the variance
    and covariance such that the relationship with depth is constant. Colors
    indicate the different chromosomes of \emph{D. melanogaster}; we have
    excluded the X chromosome (yellow points; chromosome 4 was not in the
    original study) from the regression due to large differences in average
    coverage.}

@@

\gc{To investigate whether there is a genome-wide evidence of an
  enrichment of fluctuating selection we created an
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model \gc{, as proposed by {\bf
    Machado ET AL)}.} We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.
\gc{ADD MORE HERE}

>>>>

\begin{center}
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & \gc{6?} \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
\end{tabular}
\end{center}

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated 
genome-wide $6 \times 6$ temporal covariance matrix $\mathbf{Q}$ for each of
the ten replicates. Each row of these matrices represent the temporal
covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between
\gc{the allele frequency change ($\Delta_{_{10}} p_t$) in} some initial
reference generation $s$ (the row of the matrix), and some later timepoint $t$
(the column of the matrix). \gc{We corrected these matrices for biases
created due to sampling noise, and normalize the entries for heterozygosity} (see Supplementary Material Sections
\ref{supp:ind-depth-var-corr} and \ref{supp:matrix-correction} for details on
the bias correction).\gc{ The %off-diagonal
 covariances} are expected to be zero when only drift is acting in
 \gc{a closed} population, as only linked selection can create covariance between allele
 frequency changes \parencite{Buffalo2019-io}. \gc{DO WE WANT to say
   heritable rather than linked sel} \gc{Averaging across the ten
   replicate temporal covariances matrices, Figure \ref{fig:figure-1},} we find \gc{many}
temporal covariances that are statistically significant (95\% block
bootstraps \gc{CIs} do not contain zero),
consistent  % first off-diagonal elements
with linked selection perturbing \gc{genome-wide} allele frequency changes over very short time
periods. \gc{The }covariances between \gc{all adjacent time intervals are}
positive, and then decay towards zero \gc{as we look at more distant
  time intervals} as expected when directional selection
affects linked variants' frequency trajectories until ultimately linkage
disequilibrium and additive genetic variance \gc{for fitness} decay
\parencite{Buffalo2019-io}. \gc{The temporal covariances per replicate
  are noiser but this general pattern holds}; see Supplementary
Figures XXX. \gc{ \textcite{Barghi2019-qy}'s design means that the covariances we see in adjacent time intervals
 are on average ten generations apart, given the temporal decay in
 covariance we see, the covariances on shorter
 time-scales may well be higher yet (see Supplementary Material
 Section \ref{supp:barghi-covs} for more details).}

%We visualize these covariances in Figure \label{figure-1} (A), which
%depicts the temporal covariances through time, for each of the five
%off-diagonal rows temporal covariance matrix. Each row represents the temporal
%covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between some initial
%reference generation $s$ (the row of the matrix), and some later timepoint $t$
%(the column of the matrix). For each row, the covariances at first are
%positive, and then decay towards zero as expected when directional selection
%affects linked variants' frequency trajectories until ultimately linkage
%disequilibrium and additive genetic variance for decay
%\parencite{Buffalo2019-io}. Note that per replicate, the signal is a bit
%noisier; see Supplementary Figures XXX.

%Since the \textcite{Barghi2019-qy} study sequenced each
% replicate population every ten generations, we calculate the temporal
% covariance matrix over ten-generation allele frequency changes, which we write
% as $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$. The diagonal elements of
% this temporal covariance matrix are the sum of all variances in allele
% frequency changes and pairwise covariances, e.g. element $\mathbf{Q}_{t,t} =
% \sum_{i=t}^{9} \var(\Delta p_i) + 2\sum_{i \ne j} \cov(\Delta p_i, \Delta
% p_j)$. Each off-diagonal element $\mathbf{Q}_{t,s}, \; t \ne s$ contains the
% sum of pairwise covariances, $\mathbf{Q}_{t,s} = \sum_{i=t}^{t+9}
% \sum_{j=s}^{s+9} \cov(\Delta p_i, \Delta p_j)$ (see Supplementary Material
% Section \ref{supp:barghi-covs} for more details). These off-diagonal
% covariances are expected to be zero when only drift is acting in the
% population, as only linked selection can create covariance between allele
% frequency changes \parencite{Buffalo2019-io}. Furthermore, since we cannot
% directly observe the temporal covariances between adjacent timepoints, but only
% the sums of temporal covariances, we expect the off-diagonal elements of
% $\mathbf{Q}$ to be weak. This is because the magnitude of a temporal covariance
% $\cov(\Delta p_i, \Delta p_j)$ is governed by the level of additive genetic
% variance and linkage disequilibrium that persists after $|i-j|$ generations of
% decay, which in \textcite{Barghi2019-qy}'s study design is on average 10
% generations.

@@

@@

The replicate design of \textcite{Barghi2019-qy} also allows us to quantify
another covariance: the covariance in allele frequency change between replicate
populations experiencing convergent selection pressure\gc{s}. These between-replicate
covariances are created in the same way as temporal covariances are: neutral
alleles linked to a particular fitness background experience are expected to
have allele frequency changes in the same direction if the selection pressures
are similar. We measure this through a statistic similar to a correlation,
which we call the convergent correlation; this is the ratio of average
between-replicate covariance across all pairs to the average standard deviation
across all pairs of replicates,

@@

We've calculated the convergent correlation for all rows of the replicate
covariance matrices\gc{.} Like temporal covariances, we visualize
these  %which unlike temporal covariance matrices have diagonal
%elements that are also covariances (e.g. $\cov(\Delta_{_{10}} p_{t,A},
%\Delta_{_{10}} p_{t,B})$).
through time (Figure \ref{fig:figure-2} A), with each line representing the
convergent correlation from a particular reference generation $s$ as it varies
with $t$ (shown on the x-axis). In other words, each of the colored lines
corresponds to the like colored row of the convergence correlation matrix
(upper left in Figure \ref{fig:figure-2} A). We find these
\gc{covergent covariances} decay very quickly,
from an initial \gc{value} of about 0.1 (95\% block
bootstrap confidence intervals $[0.094,  0.11]$), to around 0.01 (95\% CIs
[0.0087, 0.015]) within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate \gc{wild} populations of
\emph{Drosophila simulans} for 14 generations \gc{adapting to} a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$). \gc{GIVE
  conversion \% var due to linked selection. }

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some \gc{genome-wide} temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows (mean loci per
window 4,606, median 4,830). While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

\gc{It is unclear how strong the fluctuations would have to be to
  generate a genome-wide average signal of fluctuating selection from
  temporal covariances. For example,there many loci could still show a
  signal of fluctuating selection, but their average signals could be
  overwhelmed by other signals of fluctuating selection. To
  investigate whether there was an genome-wide excess} of loci showing evidence
  of fluctuating selection we re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B). \gc{\textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy},however, their bionomial null model does not
  include random evolutionary variation in allele frequencies. }
% =======
% We were concerned that this might be due to a flaw in our methods. To address
% this concern, we first ensured that our temporal-covariance matrix bias
% correction was working as expected. We find that it corrects the relationship
% between depth and both variance and covariance (Supplementary Figure
% \ref{suppfig:bergland-correction}) as expected. We then re-analyzed the data of
% \parencite{Bergland2014-ij} using the same seasonal fluctuating model as the
% original paper. This model is a Binomial logit-linked GLM fit per-locus, where
% the Spring/Fall seasons are encoded as a dummy variable, and are regressed on
% the frequency data. We use the same binomial weighting procedure as
% \textcite{Bergland2014-ij}, where the weights are determined by the effective
% number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and
% $d_t$ are the number of diploid individuals and the read depth at timepoint
% $t$, respectively). We fit this model on all loci marked as used in the VCF
% provided with the \textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p).
% Overall, our p-values for the Wald test for each locus closely match those of
% the original paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times
% 10^{-16}$; see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison}
% A), and the histograms of the p-values are nearly identical (Supplementary
% Figure \ref{suppfig:bergland-pvalue-comparison} B). 
% >>>>>>> d95c3549a10dc0037f40a54cb8b41f9d412ed1ed

@@

  \caption{The variance and covariances from the \textcite{Bergland2014-ij}
    study, calculated in 100kb genomic windows plotted against average depth in
    a window before and after bias correction. Each panel has a least-squares
    estimate between the variance and covariance, and the average depth.
    The bias correction procedure is correcting sampling bias in both the variance
    and covariance such that the relationship with depth is constant. Colors
    indicate the different chromosomes of \emph{D. melanogaster}; we have
    excluded the X chromosome (yellow points; chromosome 4 was not in the
    original study) from the regression due to large differences in average
    coverage.}

@@

\gc{To investigate whether there is a genome-wide evidence of an
  enrichment of fluctuating selection we created an}
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model \gc{, as proposed by {\bf
    Machado ET AL)}.} We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.
\gc{ADD MORE HERE}
